%
% LaTeX source of my resume
% =========================
%
% Heavily commented to to fit even LaTeX beginners (hopefully).
%
% See the `README.md` file for more info.
%
% This file is licensed under the CC-NC-ND Creative Commons license.
%


% Start a document with the here given default font size and paper size.
\documentclass[10pt,a4paper]{article}

% Set the page margins.
\usepackage[a4paper,margin=0.21in]{geometry}

% Setup the language.
\usepackage[english]{babel}
\hyphenation{Some-long-word}

% Makes resume-specific commands available.
\usepackage{resume}




\begin{document}  % begin the content of the document
\sloppy  % this to relax whitespacing in favour of straight margins


% title on top of the document
\maintitle{Vansh Shah}{August 02, 1994}{Last update on \today }

\nobreakvspace{0.4em}  % add some page break averse vertical spacing

% \noindent prevents paragraph's first lines from indenting
% \mbox is used to obfuscate the email address
% \sbull is a spaced bullet
% \href well..
% \\ breaks the line into a new paragraph
\noindent\href{mailto:shahvansh123.at.gmail.dot.com}{shahvansh123\mbox{}@\mbox{}gmail.com}\sbull
\textsmaller{+}1 (408)643-9381\sbull
{\newnums \href{https://github.com/vansh007}{vansh007 (Github)}\sbull
{\mewmums \href{https://www.linkedin.com/in/vansh-shah/}{www.linkedin.com/in/vansh-shah}
\\
{San Jose\sbull
California\sbull
95135\sbull
United States
}
\spacedhrule{0.0em}{-0.4em}  % a horizontal line with some vertical spacing before and after

\roottitle{Objective}  % a root section title
{\bodytext{To acquire internship in an enterprise where I can utilize my skills to achieve goals while experiencing advancement opportunities.}}

\spacedhrule{0.0em}{-0.4em}


\roottitle{Education}

\headedsection
  {\href{http://www.sjsu.edu/}{San Jose State University} {\textsmaller{GPA -- 3.53/4.00}}}
  {\textsc{California, United States}} {%
  \headedsubsection
    {Masters degree in Software Engineering}
    {Expected - December \apo17}
    {\bodytext{
    \textbf{Coursework: }Enterprise Distributed Systems, Software System Engineering, Web and Data Mining, Internet of Things, Software Quality Assurance and Testing, Smartphone Application Development.}}
}


\headedsection
  {\href{http://www.gtu.ac.in/}{Gujarat Technological University} {\textsmaller{GPA -- 3.71/4.00}}}
  {\textsc{Gujarat, India}} {%
  \headedsubsection
    {Bachelors degree in Information Technology}
    {Graduated - June \apo15}
    {\bodytext{
    \textbf{Coursework: }Data Structures, OOPS, Design and Analysis of Algorithms, Calculus, Information Security, Database, Operating Systems, Programming Languages, Advanced Computer Networks, Data Compression, Artificial Intelligence.}}
}

\spacedhrule{0.0em}{-0.4em}

\roottitle{Experience}



\headedsection  % sets the header for the section and includes any subsections
  {\href{http://www.sjsu.edu/}{San Jose State University}}
  {\textsc{California, United States}} {%
  \headedsubsection
    {Teaching Assistant - Programming Paradigms}
    {May \apo16 -- present}
    {\bodytext
    {
    \begin{itemize}
        \item Taught Programming Paradigm concepts like Procedural, Object-Oriented Programming, Functional Programming and Logic Programming to Undergraduate Computer Science class of 35-40 students.
        \item Involved in the development of new material for department courses like assignments and PowerPoint presentations.
        
        \item Performed variety of non-instructional duties, tutored students independently or in small groups, proctoring for mid semester and finals.
    \end{itemize}}}
}

\headedsection  % sets the header for a subsection and contains usually body text
  {\href{https://www.linkedin.com/company-beta/2976633/?pathWildcard=2976633}{DigimationUK}}
  {\textsc{Gujarat, India}} {%
  \headedsubsection
    {Android Developer Intern}
    {June \apo14 -- May \apo15}
    {\bodytext{
    \begin{itemize}
        \item Involved with all phases of app development from initial concepts, design, development, testing and deployment. 
        \item Participated in brainstorming and user feedback sessions to gather input to apply changes for prototype iterations. 
        \item Created SQL database structures that integrates with Android applications and web interfaces.
        \item  Integrated Google play services and Google Maps API's to a restaurant table booking app.
    \end{itemize}}}
}




\spacedhrule{0.0em}{-0.4em}

\roottitle{Academic Projects}

\headedsection  % sets the header for the section and includes any subsections
  {\href{https://github.com/shahaashay21/Amazon}{Amazon Fresh Simulation}
  \textbf{
  \small{(Node.JS | AngularJS | MongoDB | MySQL | RabbitMQ | Redis | JQuery)}}}
  {\textsc{Mar \apo16 -- May \apo16}} {%
  
    {\bodytext
    {
    \begin{itemize}
        \item Designed and developed Amazon Fresh prototype using 3 tier architecture.
        \item Customised MongoDB sharding and distributed database design with MySQL.
        \item Performed asynchronous automated testing using mocha.js framework and load testing of 100,200,500 concurrent users with 1000-2000 requests/user using JMeter.
        \item Improved performance by using combination of connection pooling, caching mechanism Redis, and advanced message queuing RabbitMQ. Implemented Dynamic pricing algorithm for seasonal rate.
    \end{itemize}}}
}

\headedsection  % sets the header for the section and includes any subsections
  {\href{https://github.com/vansh007/TEAM-MINER}{Good Buy or Bad Buy}
  \textbf{
  \small{(Python | K-means | SVM | Data Preprocessing)}}}
  {\textsc{Oct \apo16 -- Nov \apo16}} {%
  
    {\bodytext
    {
    \begin{itemize}
        \item Applied data mining techniques like K-Means and Supervised Learning (Support vector machines) on the cars data-set to determine whether the car bought in the auction was a good buy or not.
        \item Performed preprocessing on the data-set and obtained 85-90 \% accuracy in the result which was plotted on the graph.
        
    \end{itemize}}}
}

\headedsection  % sets the header for the section and includes any subsections
  {\href{https://github.com/vansh007}{Udemy Test Automation}
  \textbf{
  \small{(Selenium | Java | Appium | UIAutomator)}}}
  {\textsc{Sep \apo16 -- Nov \apo16}} {%
  
    {\bodytext
    {
    \begin{itemize}
        \item Created and executed automated software test plans, cases and scripts to uncover, identify and document problems in a website and a mobile app named Udemy.
        \item Extensively automated regression and functional test suites by developing over 20 test cases using Selenium and JAVA.
        \item Developed Keyword Driven and Data Driven frameworks to retrieve test actions, test data from Excel files
        
        
    \end{itemize}}}
}



\headedsection  % sets the header for the section and includes any subsections
  {\href{https://github.com/pendawleabhay/LibraryManagementSystem}{Library Management System}
  \textbf{
  \small{(Spring MVC | Java | Google Books API | Aws | MySQL - RDS)}}}
  {\textsc{Nov \apo16 -- Dec \apo16}} {%
  
    {\bodytext
    {
    \begin{itemize}
        \item Designed web application which had functionalities like searching, borrowing, returning, circulating, wait listing, cataloguing books and collecting fines.
        \item Directly involved in the development efforts to produce custom data driven multi-tiered applications and Web Services.
        \item Implemented Google Books API so that Librarian can simply add books by its ISBN number.
        
    \end{itemize}}}
}


\spacedhrule{0.0em}{-0.4em}

\roottitle{Skills}


  {
  \begin{itemize}
      \item Software design and implementation, with(in) a team.  Big fan of Agile methodologies (Scrum and Kanban).
      \item Java, \nsp Python, Javascript (mostly Angular and jQuery), C, C\#, Spring MVC, R. Apache, RabbitMQ, Redis Cache.
      \item Web Technologies and Database: \acr{HTML+CSS}, \acr{XML},\acr{Passport.js}, \acr{JSP}, \acr{REST}, \acr{SOAP}. My\acr{SQL}, MongoDB, IBM DB2, sqllite.
      \item Cloud and Testing: AWS, IBM Bluemix, Google App Engine, Node-red,and \acr{EC}2 | JUnit, Mocha.js, Selenium, Nagios Xl.
      \item Event coordinator at ISO(Indian student Organisation) and active participant in intramural at school.
      
  
  \end{itemize}  
  }



\spacedhrule{0.0em}{-0.4em}



\end{document}
\documentclass[oneside]{book}